### 2016-01-19 paper.tex
Name subsection 'near-wake...' per @nearyvs suggestion
Thanks --> due

\subsection*{Wake characteristics}

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine thanks to lower rotor drag coefficient and
blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade tip
vortex shedding are relatively weaker, which is likely an effect of the RM2's
lower solidity and tapered blades.

>>>>

\subsection*{Near-wake characteristics}

The mean velocity field at a tip speed ratio $\lambda=3.1$, 1 m downstream
($x/D=0.93$) is plotted in Fig.~\ref{fig:meancontquiv}. The mean streamwise
velocity deficit is markedly more symmetric than that of the UNH-RVAT, with
lower acceleration around the turbine due to the lower rotor drag coefficient
and blockage ratio \cite{Bachant2015-JoT}. We also see that the effects of blade
tip vortex shedding are relatively weaker, which is likely an effect of the
RM2's lower solidity and tapered blades.
